---
title: "DAT Project Group E"
subtitle: "DASC 360: Multivariate Data Analysis"
author: "Bryce Pacourek, Tyler Johnson, Reilly Kurth, Munir Abdikadir"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    number_sections: false
    toc_float:
      collapsed: false
      smooth_scroll: false
mainfont: TimesNewRoman
sansfont: TimesNewRoman
monofont: TimesNewRoman
---

#### Load Relevant R Libraries
```{r warning=FALSE, message=FALSE}
library(rmarkdown); library(knitr); library(moments); 
library(scatterplot3d); library(corrplot); library(pso)
library(psych); library(GPArotation); library(lavaan)
```


### Data Source
We accessed our data from the United Nations Sustainable Development Goals Indicators Database. https://unstats.un.org/sdgs/dataportal

## 1. Load Data
```{r}
# code
```

## 2. Describe source and process used to download data
answer


### Data Dimensions
Introductory sentence...
```{r}
Head()
```

## Predictor Dimensions
Descriptions of each dimension

## Response Dimensions
Descriptions of each dimension


### Data Adjustments
Need to remove any dims/vars? Create dummy vars?

## Describe what needs to be done
Answer
