---
title: "DAT Project Group E"
subtitle: "DASC 360: Multivariate Data Analysis"
author: "Bryce Pacourek, Tyler Johnson, Reilly Kurth, Munir Abdikadir"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    number_sections: false
    toc_float:
      collapsed: false
      smooth_scroll: false
mainfont: TimesNewRoman
sansfont: TimesNewRoman
monofont: TimesNewRoman
---

#### Load Relevant R Libraries
```{r warning=FALSE, message=FALSE}
library(rmarkdown); library(knitr); library(moments); 
library(scatterplot3d); library(corrplot); library(pso)
library(psych); library(GPArotation); library(lavaan)
```


## Data Source
We accessed our data from the [World Bank World Development Indicators](https://databank.worldbank.org/)

### 1. Load Data
```{r}
read.csv("https://raw.githubusercontent.com/kurt8267/DASC360-Group-E-Project-/refs/heads/main/35943a83-804a-4f98-9389-0cdbecb276de_Data.csv")
```

## Describe source and process used to download data
There is a graphical user interface where countries, variables, and years of collection can be selected. Data can be exported as an Excel file or CSV.


## Data Dimensions
We downloaded any dimensions that seemed promising so we could narrow them down to the best and most complete.
```{r}
head()
```

### Predictor Dimensions
Descriptions of each dimension

### Response Dimensions
Descriptions of each dimension


### Data Adjustments
We need to transform the data from long to wide, and remove most dimensions.