---
title: "DAT Project Group E"
subtitle: "DASC 360: Multivariate Data Analysis"
author: "Bryce Pacourek, Tyler Johnson, Reilly Kurth, Munir Abdikadir"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    number_sections: false
    toc_float:
      collapsed: false
      smooth_scroll: false
mainfont: TimesNewRoman
sansfont: TimesNewRoman
monofont: TimesNewRoman
---

#### Load Relevant R Libraries
```{r warning=FALSE, message=FALSE}
library(rmarkdown); library(knitr); library(moments); 
library(scatterplot3d); library(corrplot); library(pso)
library(psych); library(GPArotation); library(lavaan)
```


## Data Source
We accessed our data from the [World Bank World Development Indicators](https://databank.worldbank.org/)

### 1. Load Data
```{r}
data_raw <- read.csv("https://github.com/kurt8267/DASC360-Group-E-Project-/raw/refs/heads/dat-2026-10-06/dat-data-trimmed-long.csv",
                     quote = "")
```

## Describe source and process used to download data
There is a graphical user interface where countries, variables, and years of collection can be selected. Data can be exported as an Excel file or CSV.


## Data Dimensions
We downloaded any dimensions that seemed promising so we could narrow them down to the best and most complete.
```{r}
head(data_raw)
```

### Predictor Dimensions
- Access to electricity (% of population)
- UHC service coverage index - a single summary measure scored from 0 to 100 that tracks a country's
- average coverage of essential health services 
- Out-of-pocket expenditure (% of current health expenditure)
- Food production index (2014-2016 = 100)
- Population density (people per sq. km of land area)
- People using at least basic sanitation services (% of population) - 2 missing cases
- Current health expenditure per capita (current US$)
- Domestic general government health expenditure (% of GDP)
- Domestic private health expenditure (% of current health expenditure)

### Response Dimensions
- Mortality rate, under-5 (per 1,000 live births)
- Suicide mortality rate (per 100,000 population)
- Birth rate, crude (per 1,000 people)
- Cause of death, by communicable diseases and maternal, prenatal and nutrition conditions (% of total)
- Death rate, crude (per 1,000 people)


### Data Adjustments
We need to transform the data from long to wide, and remove most extraneous dimensions.